### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
made a succesful replication ratio table.

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "AWITHSUPERSCRIPT replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = TRUE, placement= "h")

### add a midrule before total

>>>>

# Changing column names to be less computer speak-y looking
colnames(replication_ratio_table) <- c("Many Labs Version", "N Total", "N Replicated",
                                       "Replication Ratio")

# converting columns to string to then add a superscript to one of the elements
# in the table.
replication_ratio_table$"N Replicated" <- as.character(replication_ratio_table$"N Replicated")

# adding a superscript for a later footnote
replication_ratio_table$"N Replicated"[3] <- "$3^a$"

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = FALSE, placement= "h", midrules = 4)
